\global\long\def\y{\mathbf{y}}


The Integer Linear Program we have described above has an exponential
number of (cycle) constraints. Hence, simply passing the ILP to an
off-the-shelf ILP solver is not practical for all but the smallest
sentences. For this reason the original {}``Optimal Decoding'' work
only considers sentences up to a length of 8 words. However, recent
work~\citep{riedel06incremental} has shown that even exponentially
large decoding/search problems can efficiently solved using ILP solvers
if a so-called Cutting-Plane Algorithm~\citep{dantzig54solution}
is used.%
\footnote{It is worth mentioning that Cutting Plane Algorithms have been successfully
applied for solving very large instances of the Travelling Salesman
Problem, a problem essentially equivalent to the decoding in Model
4 {[}cite someone?.%
} 
% In the following we will present a Cutting Plane algorithm for IBM
% Model 4:
% \begin{enumerate}
% \item Construct ILP $I$ without cycle constraints

% \begin{enumerate}
% \item \textbf{do}

% \begin{enumerate}
% \item solve $I$ and assign to solution $\y$
% \item find cyclic paths in solution $\y$
% \item add corresponding cycle constraints to $I$
% \end{enumerate}
% \textbf{until} no more cyclic paths can be found

% \item \textbf{return} $\y$
% \end{enumerate}
% \end{enumerate}
In our case the Cutting Plane algorithm starts with a subset of the complete set
of constraints, namely all constraints but the (exponentially many)
cycle constraints. The corresponding ILP is solved by a standard ILP
solver, and the solution is inspected for cycles. If it contains
no cycles we are done (we have found the true optimum: the solution
with highest score that does not violate any constraints). If the
solution does contain cycles, the corresponding constraints are added
to the ILP which is in turn solved again. This process is continued
until no more cycles can be found. 

% It is difficult to make claims about a guaranteed worst-case runtime
% (or number of iterations) of this algorithm. However, if the linear
% scoring function (in other words, the translation model and language
% model parameters) already provides a preference for cycle-free solutions,
% we can expect this algorithm to be efficient. For example, if we assume
% that the translation/distortion model has a very strong preference
% for monotonic solutions then clearly the highest scoring solution
% is likely to be cycle-free.




%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ilp-mt"
%%% End: 
