%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End: 

Semantic Role Labelling~\citep[SRL, ][]{carreras05introduction}
is generally understood as the task of identifying the semantic arguments
and modifiers of a given predicate token in a setence. For example,
for
\begin{quote}
Ms. {[}Haag$_{Player}$] plays {[}Elianti$_{Role}$].
\end{quote}
we are to find out that for the predicate token {}``plays'' the
token {}``Haag'' is referring to the player of the play event, and
{}``Elianti'' is refeerring to the role {}``Elianti'' is playing
(see figure ?).%
\footnote{This is the dependency-based formulation of SRL.%
} SRL is considered as a key task for applications that require to
answer {}``Who'', {}``When'', {}``What'' etc. questions, such
as Information Extraction, Question Answering and Summarization. 

Any real-world SRL system needs to make several decisions, either
explicitely or implicitely: which are the predicate tokens of a sentence
(predicate identification), which are the tokens that have semantic
roles with respect to these predicates (argument identification),
which are the roles these tokens play (argument classification), and
which is the sense of the predicate (sense disambiguation).

In this paper we use Markov Logic, a Statistical Relational Learning
framework that combines First Order Logic and Markov Networks, to
develop a joint probabilistic model over all decisions mentioned above.
This has the following reasons. %% TODO: a bit disconnected here

First, it allows us to readily capture \emph{global correlations}
between decisions, such as the constraint that a predicate can only
have one agent. This type of correlations has been successfully been
exploited in several previous SRL systems~\citep{toutanova05joint,punyakanok05generalized}. 

Second, we can use the joint model to evaluate the benefit incorporating
decisions into the joint model that either have not received much
attention within the SRL community (predicate identification and sense
disambiguation), or been largely made in isolation (argument classification
for \emph{all} predicates of a sentence). 

Third, our Markov Logic model is essentially a template that describes
a class of Markov Networks, one for each SRL problem we encounter.
Algorithms can perform inference in terms of this template without
ever having to fully instantiate the complete Markov
Network~\citep{riedel08improving}. This can dramatically improve the efficiency of an SRL system when
compared to a propositional approach such as Integer Linear Programming.

%% SR: This bit is just to remind me that we should sell this point,
%% too. It might not make it into the paper as is, though!
Fourth, by framing our problem in Markov Logic we provide a natural
upgrade path for the consideration of richer models. For example, it
would be relatively straight-forward to include a Relation Extraction
component into our model, or the prediction of the next speech act in a
dialogue system.

Finally, when it comes to actually building an SRL system with Markov
Logic (say, in order to reproduce this work) there are ``only''
four things left for us to do: preparing input data files, converting
output data files, and triggering learning and inference. The remaining
work can be done by an off-the-shelf Markov Logic interpreter. This
is to be contrasted to Pipeline systems where several components need
to be trained and connected, or ILP approaches that in which we need
to write additional wrapper code to generate ILPs.

Empirically we find that our system is highly competetive---our best
model would appear on par with the best entry in the CoNLL 2008
shared task open track, and at the 4th place when compared to systems
that use dedicated parsers; this is remarkable in the sense that the
top 3 systems use optimized parsers while we use the MALT
dependencies provided in the open track dataset.  
% We use charniak parses


We also observe that by integrating frame disambiguation into the
joint SRL model, and by extracting all arguments for all predicates in a
sentence simultanously, significant improvements compared to pipelined
system can be achieved. These improvements are particular dramatic in
the case of out-of-domain data, suggesting that a joint approach helps
to increase the robustness of SRL. 

Last but not least, we show that our system is significantly faster
than an equivalent ILP-based approach (maybe also faster than the
pipeline?). 

Our paper is organized as follows: we first introduce Markov Logic,
then we present our model in terms of Markov Logic. How this model
will be evaluated is explained in section ? with the corresponding
evaluation presented in section ? We conclude in section ?.


